### 2019-10-28 README.Rmd
bug fixes

As of right now, `pdp` exports four functions:

@@

  * `topPredictors()` extract most "important" predictors from various types of fitted models. (Will soon be replaced by functionality from [vip](https://koalaverse.github.io/vip/index.html).)

@@

# Alternatively, you can install the development version from GitHub:
# install.packages("remotes")
remotes::install_github("bgreenwell/pdp")
```

>>>>

As of right now, `pdp` exports the following functions:

@@

  * ~~`topPredictors()` extract most "important" predictors from various types of fitted models.~~ see [vip](https://koalaverse.github.io/vip/index.html) instead for a more robust and flexible replacement;

  * `exemplar()` - construct an exemplar record from a data frame (**experimental** feature that may be useful for constructing fast, approximate feature effect plots.)

@@

# Alternatively, you can install the development version from GitHub:
if (!("remotes" %in% installed.packages()[, "Package"])) {
  install.packages("remotes")
}
remotes::install_github("bgreenwell/pdp")
```
